---
title: "Ashrae Great Energy Predictor III - GAM"
author: "Oliver Mueller"
output: html_notebook
---


# Initialize notebook

Load required packages.
```{r load packages, warning=FALSE, message=FALSE}
library(RMySQL)
library(tidyverse)
library(lubridate)
library(ggthemr)
library(tidymodels)

```

Set up workspace, i.e., remove all existing data from working memory, initialize the random number generator, turn of scientific notation of large numbers, set a standard theme for plotting.

```{r setup}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rm(list=ls())
set.seed(42)
options(scipen=10000)
ggthemr('fresh')

```


# Problem description
In this Kaggle competition, you will develop accurate models of metered building energy usage in the following areas: electricity (meter 0), chilled water (meter 1), steam (meter 2), and  hot water (meter 3). The data comes from over 1,000 buildings over a three-year time period.


# Load data

Establish connection to MySQL database.

```{r}
driver <- dbDriver("MySQL")

connection <- dbConnect(driver,
                        host ="manila.uni-paderborn.de", 
                        port =3306,
                        dbname = "ashrae",
                        user = "student", password = "upb123!")

```

Read training set from MySQL database. To limit run time of our models, we will focus on electricity consumption (meter 0) of the first 100 buildings.

```{r}
data <- dbGetQuery(connection, statement = "
                  SELECT *
                  FROM train 
                  WHERE meter = 0
                  AND building_id <= 100")

weather <- dbGetQuery(connection, statement = "
                  SELECT *
                  FROM weather_train")

building_metadata <- dbGetQuery(connection, statement = "
                  SELECT *
                  FROM building_metadata")

```


# Prepare data

Transform data types, extract information from timesteps, handle missing values, join data frames, train/test split, etc.

```{r}
data_joined <- data %>% 
  inner_join(building_metadata, by = "building_id") %>% 
  inner_join(weather, by = c("site_id", "timestamp")) %>% 
  mutate(
    site_id = factor(site_id),
    building_id = factor(building_id),
  ) %>% 
  select(-meter, -site_id, -floor_count)

data_split <- initial_split(data_joined, prop = .8, strata = meter_reading)
train <- training(data_split)
test  <- testing(data_split)

test <- test %>% 
  mutate(
    id = str_c(building_id, " - ", timestamp)
  )

solution <- test %>% 
  select(id, meter_reading)

sample_submission <- test %>% 
  select(id) %>% 
  mutate(
    meter_reading = 0
  )

test <- test %>% 
  select(-meter_reading)

```

Backup/restore prepared data.

```{r}
write_csv(train, "train.csv")
write_csv(test, "test.csv")
write_csv(solution, "solution.csv")
write_csv(sample_submission, "sample_submission.csv")

```

