---
title: "Data Science for Business - Week 08: Kaggle Competition on Prediction of Elecricity Consumption"
author: "Oliver Mueller"
output: html_notebook
---

# Initialize notebook

Load required packages.

```{r load packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(ggthemr)
library(tidymodels)
library(naniar)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rm(list=ls())
set.seed(42)
options(scipen=10000)
ggthemr('fresh')
doParallel::registerDoParallel()

train <- read_csv("train.csv")
test <- read_csv("test.csv")
```

```{r}
test$year_built <- factor(test$year_built)

str(test)

```

# Explore data

Summary stats.

```{r}
summary(train)

```

Analyze data quality (esp. missing values).

```{r}
vis_miss(sample_frac(train, 0.01))

```

Histogram of `meter_reading`.

```{r}
ggplot(data=filter(train)) +
  geom_histogram(mapping = aes(x=meter_reading), color="white")

```

Explore numerical predictors.

```{r}
ggplot(data=train) +
  geom_histogram(mapping = aes(x=square_feet), color="white")

```

Explore categorical predictors.

```{r}
ggplot(data=train) +
  geom_bar(mapping = aes(x=primary_use)) + 
  theme(axis.text.x = element_text(angle = 90))

```

```{r}
ggplot(data=train) +
  geom_bar(mapping = aes(x=as.factor(year_built))) + 
  theme(axis.text.x = element_text(angle = 90))

```

Explore bivariate relationships between target and categorical predictors.

```{r}
ggplot(data=train) +
  geom_boxplot(mapping = aes(y=meter_reading, x=primary_use)) +
  scale_y_log10() + 
  theme(axis.text.x = element_text(angle = 90))

```


```{r}
ggplot(data=train) +
  geom_boxplot(mapping = aes(y=meter_reading, x=as.factor(year_built))) +
  scale_y_log10() + 
  theme(axis.text.x = element_text(angle = 90))

```

Explore bivariate relationships between target and numerical predictors.

```{r}
ggplot(data=sample_frac(train, 0.1)) +
  geom_point(mapping=aes(x=square_feet, y=meter_reading), alpha=0.1) +
  geom_smooth(mapping=aes(x=square_feet, y=meter_reading), method="lm")

```
