---
title: "DS4B Kaggle Competition - Random Forest"
author: "Dennis Wüppelmann"
output: html_notebook
---
# Initialize notebook

```{r load packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(ggthemr)
library(tidymodels)
library(naniar)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rm(list=ls())
set.seed(456)
options(scipen=10000)
ggthemr('fresh')
doParallel::registerDoParallel(cores = 8)

train <- read_csv("train.csv")
test <- read_csv("test.csv")

```

# Modeling

## Model

Create a `model` specification for tree-based models (`rand_forest` or `boost_tree`) with tunable hyperparameters.

```{r}
electricity_model <- rand_forest(mode = "regression",  mtry = 10,  trees = 600) %>%
  set_engine("ranger")

electricity_model

electricity_recipe <- 
  recipe(meter_reading ~ ., data = train) %>%
  #step_sample(size = 0.7) %>% # sample from the training data for performance reasons
  step_mutate(
    month = as.factor(lubridate::month(timestamp)),
    dow = as.factor(lubridate::wday(timestamp)),
    hour = as.factor(lubridate::hour(timestamp))
  ) %>% 
  step_rm(timestamp, building_id, cloud_coverage) %>% 
  step_medianimpute(all_numeric_predictors()) %>% 
  step_modeimpute(all_nominal())

electricity_recipe

```

`Bake` the recipe, just the check whether it produces the expected results.

```{r}
tmp <- electricity_recipe %>% 
  prep() %>% 
  bake(head(train))

head(tmp)

```

## Workflow

The final specification is for the `workflow`, which glues together the `model` and `recipe`.

```{r}
electricity_wflow <- workflow() %>% 
  add_model(electricity_model) %>% 
  add_recipe(electricity_recipe)

electricity_wflow

```

## Resampling

We use `3-fold cross validation` for tuning hyperparameters and calculating accuracy.

```{r}
folds <- vfold_cv(train, v = 3)

```

## Sample with no tuning
```{r}
electricity_fit <- electricity_wflow %>% 
  fit_resamples(folds)

collect_metrics(electricity_fit)
```

## Hyperparameter Search

Let's use a `random grid` with a defined `size` for sampling hyperparameter values.

```{r}
hyp_grid <- grid_random(mtry(range = c(3,15)), trees(c(10,1000)), size = 10)
hyp_grid

electricity_tuned <- electricity_wflow %>% 
  tune_grid(
    resamples = folds,
    grid = hyp_grid
)
collect_metrics(electricity_tuned)
```


# Upload to Kaggle

Now we retrain our model with the best hyperparameters and without resampling on the full training set and use it to make predictions on the test set.

```{r}
electricity_best <- finalize_workflow(electricity_wflow, select_best(electricity_fit, "rmse"))

electricity_best_fit <- electricity_best %>% 
  fit(train)

preds <- predict(electricity_best_fit, new_data = test)

```

Finally, we extract the predictions (`preds`) for the test set, bind it together with the `id` columns, rename the column headings, and export the results as a CSV file.

```{r}
submission <- test %>%
  select(id) %>% 
  bind_cols(preds)

names(submission) <- c("id", "meter_reading")

write_csv(submission, "my_submission_rdmf.csv")

```

# Your Task

Tune a tree-based model to make it to the top of our Kaggle leaderboard!
