---
title: "DS4B Kaggle Competition - splines"
author: "Dennis Wüppelmann"
output: html_notebook
---
# Initialize notebook

```{r load packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(ggthemr)
library(tidymodels)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
rm(list=ls())
set.seed(123)
options(scipen=10000)
ggthemr('fresh')
doParallel::registerDoParallel()

```


```{r}
train <- read_csv("train.csv")
test <- read_csv("test.csv")

```


```{r}
electricity_model <- linear_reg() %>% 
  set_engine("lm")

electricity_model

```

## Recipe

Next, we specify a `recipe` for data preprocessing.

```{r}
electricity_recipe <- 
  recipe(meter_reading ~ ., data = train) %>%
  step_mutate(
    month = as.factor(lubridate::month(timestamp)),
    dow = as.factor(lubridate::wday(timestamp)),
    #weekend = as.factor(ifelse(lubridate::wday(timestamp)<6,"Weekday","Weekend"))
  ) %>% 
  step_rm(timestamp, building_id) %>% 
  step_impute_median(all_numeric(), -all_outcomes()) %>% 
  step_impute_mode(all_nominal(), -all_outcomes()) %>%
  step_normalize(all_numeric(), -all_outcomes()) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_ns(all_numeric_predictors())

electricity_wflow <- workflow() %>% 
  add_model(electricity_model) %>% 
  add_recipe(electricity_recipe)

electricity_wflow
```

## Workflow

The final specification is for the `workflow`, which glues together the `model` and `recipe`.
```{r}
folds <- vfold_cv(train, v = 3)

electricity_fit <- electricity_wflow %>% 
  fit_resamples(folds)

collect_metrics(electricity_fit)
```

```{r}
folds <- vfold_cv(train, v = 3)
lambda_grid <- grid_regular(
  deg_free(range = c(1, 10)), 
  levels = 20
  )

electricity_tuned <- electricity_wflow %>% 
  tune_grid(
    resamples = folds,
    grid = lambda_grid
)


show_best(electricity_tuned, "rmse")
```

# Upload to Kaggle

We retrain our model without resampling on the full training set and use the model to make predictions on the test set.

```{r}
electricity_best <- finalize_workflow(electricity_wflow, select_best(electricity_fit, "rmse"))

electricity_best_fit <- electricity_best %>% 
  fit(train)

preds <- predict(electricity_best_fit, new_data = test)

```

Finally, we extract the predictions (`preds`) for the test set, bind it together with the `id` columns, rename the column headings, and export the results as a CSV file.

```{r}
submission <- test %>%
  select(id) %>% 
  bind_cols(preds)

names(submission) <- c("id", "meter_reading")

write_csv(submission, "my_submission_spline_all.csv")

```

# Your Task

Now it's your turn. Try one or more of the following strategies:

1.  `Feature engineering`, that is,

    -   *transform* existing variables (see <https://recipes.tidymodels.org/reference/index.html#section-step-functions-individual-transformations>),

    -   use different *imputations* for missing values (see <https://recipes.tidymodels.org/reference/index.html#section-step-functions-imputation>),

    -   create *new features* from the original variables (e.g., weekday or weekend?),

    -   create *interaction terms* (see <https://recipes.tidymodels.org/reference/step_interact.html>),

2.  Use `LASSO` instead of LM. To tune the `lambda` penalty term, you have to extend the above code by adding code for hyperparameter tuning (see code from Week 6).

3.  Use non-linear `splines` (see Week 7). You can fit natural splines by adding `step_ns` steps to the recipe and try different `deg_free` parameter values (see <https://recipes.tidymodels.org/reference/step_ns.html>). The best deg\_free parameter value can also be determined through tuning.

